|

### 2017-10-07 manuscript.Rmd
one typo leading to one sentence changed
Keep original order, but add a just works intro paragraph.

   Docker permits convenient access to pre-configured and create
   _binary_ images that "just work".  This allows R users to access a
   wider-variety of ready-to-use environments than the R Project
   itself provides.  For example, R users on Windows may run RStudio
   Server or Shiny Server locally just by launching a single command
   (once Docker itself is installed), access R-devel without affecting
   their local system and more.

@@

@@

The `docker run` option `-p` sets the port on which RStudio will appear, 8787 is
the RStudio default. Many academic and commercial cloud providers make it
possible to execute such code snippets when a container is launched, without
ever needing to `ssh` into the machine. The user may log into the server merely
by pasting its IP address or DNS name (followed by the chosen port, e.g. `:8787`)
into a browser and entering the
appropriate password.  This provides the user with a familiar,
interactive environment running on a remote machine while requiring
a minimum of expertise.

>>>>

@@

Docker permits convenient access to pre-configured and create
_binary_ images that "just work."  This allows R users to access a
wider-variety of ready-to-use environments than the R Project
itself provides.  For example, R users on Windows may run RStudio
Server or Shiny Server locally just by launching a single command
(once Docker itself is installed), access R-devel without affecting
their local system and more.  Here, we detail the some of the principle
use cases motivate these containerized versions of R environments
and the design principles that help make them work.

The `docker run` option `-p` sets the port on which RStudio will appear, 8787 is
the RStudio default (adding your user to the docker group to avoids the
nedd for a `sudo` command to call `docker`: `sudo usermod -g docker $USER`). 
Many academic and commercial cloud providers make it
possible to execute such code snippets when a container is launched, without
ever needing to `ssh` into the machine. The user may log into the server merely
by pasting its IP address or DNS name (followed by the chosen port, e.g. `:8787`)
into a browser and entering the appropriate password.  
This provides the user with a familiar,
interactive environment running on a remote machine while requiring
a minimum of expertise.

@@
